SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2021-01-20 maintex.tex
edits to the discussion

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. {\it We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts.} \textbf{Our results indicate that merger induced gas-inflows are responsible for elevating the central sSFR in galaxy pairs. }
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic). From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line. (\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies. }
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\textbf{
We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD). The code used the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA.
}

\textbf{
For each MaNGA 1\arcsec$\times$1\arcsec\ spaxel, we use our spectral fitting code, {\sc spfit}, to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
}

\textbf{
The are a few differences between {\sc SPFIT} and the previous spectral fitting codes designed for the MaNGA project; the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc Pipe3D} \citep{Sanchez:2016a, Sanchez:2016b}. {\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels while the {\sc DAP} and {\sc Pipe3D} leaves the data in its original 0.5\arcsec $\times$ 0.5\arcsec\ format. Each code uses a slightly different SSP library. The {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019}, {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES \citep{Sanchez-Blazquez:2006} libraries, and {\sc SPFIT} uses the MIUSCAT library which is the combination of the MILES, CaT \citep{Cenarro:2001}, and Indo-U.S. stellar libraries \citep{Valdes:2004}. Both {\sc SPFIT} and the {\DAP} simultaneously fits emission lines and the stellar continuum while {\sc PIPE3D} only fits the emission lines.
}

\subsection{\textbf{Selecting Star Forming Galaxies}}\label{sec:sf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
\tablecaption{Pair Catalog}
\tablehead{
\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
}
\decimals
\startdata
7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
\enddata
\tablecomments{
(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass. \\ \\
(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
}
\label{tab:pair}
\end{deluxetable*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:pair}.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within 0.1 dex in stellar mass limit, \textbf{0.025 in redshift, 20\% \reff}, and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. With these requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found. Only 5 of the paired galaxies required an extra iteration to find 20 controls.

@@

\textbf{
The signal to noise ratio of the data will fall with wide galactocentric radii. MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample. These are not hard limits, data will exist beyond these radii, especially along the semi-minor axis of galaxy; however, the data beyond these limits may be unreliable due to low signal to noise. To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line. 
}

\textbf{
We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}. This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
}

@@

Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. Within each radius bin we take the median of the specific star formation rate.

The profiles' errors are the standard error of the mean of the data within each radius bin. \textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
\begin{equation}
\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
\end{equation}
where $\sigma$ is the standard deviation and $n$ is the sample size.} We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample).} {\it While the MaNGA sample is limited spatially to 1.5$-$2.5 \reff\, the spaxels along the semi-minor axis of a galaxy will be able to extend beyond that range because of the galaxy's inclination angle, sin($i$).}

@@

In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5. Within each stellar mass bin, we create a median profile of log(sSFR) as a function of \reff-scaled galactocentric distance for both paired and control galaxies. The control profiles are constructed using all available control galaxies within each mass bin. The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin. We show these stacked profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}. Star formation in the control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with stellar mass, consistent with previously published results using the MaNGA survey \citep{Belfiore:2018}. In contrast, the paired galaxies show flatter sSFR profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5, which still show some central quenching.

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.2 \reff. In the outskirts of the pairs beyond 1.2 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

\textbf{ 
We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}. We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR. We do see that the pair-control offsets are lightly suppressed using the \ewha. 
}

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the plain mass ratio. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff. The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels. Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made. The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}

The difference profiles are shown to be centrally enhanced by $\sim$0.3 $\pm$ 0.1 dex. Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.10$-$0.15 dex higher than the sample average.

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex. As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.

@@

\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split difference profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0. Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers. We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex. The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel. Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.}

@@

In \textbf{bottom left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins. \textbf{The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0. When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair. In major mergers, the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.}

>>>>

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.25 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts. \textbf{Our results are consistent with the idea that merger induced gas-inflows are capable of triggering elevated star formation in paired galaxies. }
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. \textbf{(\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies.} The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic).}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\textbf{
We use our own {\sc idl} based spectral fitting code, {\sc spfit}\footnote{\url{https://github.com/fuhaiastro/spfit}}, to model the spectra from the MaNGA datacubes \citepalias{Fu:2018}. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD). 
}

\textbf{
{\sc SPFIT} re-bins the MaNGA datacubes into 1\arcsec $\times$ 1\arcsec\ pixels to remove the covariances between neighboring pixels. This is in contrast with previous spectral fitting codes designed for the MaNGA survey like the MaNGA {\sc DAP} \citep{Belfiore:2019} and {\sc PIPE3D} \citep{Sanchez:2016a, Sanchez:2016b} which uses the original 0.5\arcsec $\times$ 0.5\arcsec\ grid. Within each 1\arcsec$\times$1\arcsec\ pixel, we use {\sc spfit} to get measurements of emission line fluxes, equivalent widths, velocities, and velocity dispersions of 19 emission lines and measurements of stellar masses, ages, [Fe/H], and the kinematics of the stellar populations.
}

\textbf{
The code uses the SSP templates from the MUISCAT library \citep{Vazdekis:2012} which allows a spectral range of 3465$-$9469 \AA\ with a uniform spectral resolution of FWHM $=$ 2.5 \AA. This MIUSCAT library is the combination of the MILES \citep{Sanchez-Blazquez:2006}, CaT \citep{Cenarro:2001}, and Indo-U.S. stellar libraries \citep{Valdes:2004}. The MaNGA {\sc DAP} uses the MILES-HC (Hierarchically Clustered MILES templates) library \citep{Westfall:2019} and {\sc PIPE3D} library uses the GSD156 library \citep{Cid-Fernandes:2013} which is built from the GRANADA \citep{Martins:2005} and MILES libraries.
}

\subsection{Selecting Star Forming Galaxies}\label{sec:sf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
%\tablecaption{Pair Catalog}
%\tablehead{
%\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
%\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
%}
%\decimals
%\startdata
%7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
%7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
%7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
%7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
%7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
%8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
%8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
%8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
%8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
%8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
%\enddata
%\tablecomments{
%(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) 
%stellar mass. \\ \\
%(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
%}
%\label{tab:pair}
%\end{deluxetable*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{table1.tex}

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:coords}.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within 0.1 dex in stellar mass limit, \textbf{0.025 in redshift, 20\% \reff}, and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. With these requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found. \textbf{39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations. }

@@

\textbf{
The signal to noise ratio of the data will decrease with wide galactocentric radii. MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample. These are not hard limits, data will exist beyond these radii, especially along the semi-minor axis of galaxy; however, the data beyond these limits may be unreliable due to low signal to noise. To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line. We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}, which effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
}

@@

Once the geometries of the galaxies are set, we can build azimuthally averaged radial profiles. The spaxels are binned into radius increments of 0.2 \reff\ from 0.0$-$2.6 \reff. Within each radius bin we take the median of the specific star formation rate. We build an azimuthally averaged radial profile for each MaNGA star forming galaxy and later stack and differentiate these profiles in the subsequent analysis.

\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample). This means that there will be fewer selected spaxel beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff. We decide to still extend our radial profiles out to 2.5 \reff, but emphasize that the data beyond 1.5 \reff\ is lower in quality. }

@@

In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5. Within each stellar mass bin, we create a median profile of log(sSFR) as a function of \reff-scaled galactocentric distance for both paired and control galaxies. The control profiles are constructed using all available control galaxies within each mass bin. The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin. \textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
\begin{equation}
\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
\end{equation}
where $\sigma$ is the standard deviation and $n$ is the sample size.}

We show these stacked profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}. Star formation in the control galaxies are quenched in their centers with respect to their disks and the difference between the sSFR in their centers and their disks increases with stellar mass, consistent with previously published results using the MaNGA survey \citep{Belfiore:2018}. In contrast, the paired galaxies show flatter sSFR profiles where the level of the sSFR remains roughly consistent across their disks except for paired galaxies with stellar masses above \logm\ $=$ 10.5, which still show some central quenching.

We then take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the difference profiles really represent a ratio between the pairs and controls in linear space). This gives us the difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). Across all stellar mass bins, the sSFR of paired galaxies are centrally enhanced by $\sim$0.3$\pm$0.1~dex, which gradually falls to zero around $\sim$1.5 \reff. In the outskirts of the pairs beyond 1.5 \reff, the pairs feature lightly suppressed sSFR of 0.0$-$0.1 dex. All of the mass ranges except for the highest mass range, \logm\ $=$ 11.0$-$11.5, trend closely to the median profile. For the most massive galaxies, \logm\ $=$ 11.0$-$11.5, the enhancement to the sSFR within 0.5 \reff\ is significantly higher than the median profile (reaching 0.5$-$0.6 dex). As will be discussed in \S~\ref{sec:tailored}, we believe this elevated enhancement in the highest mass bin is driven by more compact mergers instead of stellar mass.

@@

\textbf{ 
We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}. We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR. We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex. 
}

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff. The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels. Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made. The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}

The difference profiles are shown to be centrally enhanced by $\sim$0.20$-$0.25 $\pm$ 0.1 dex. Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.4 dex higher than the sample average.

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.0$-$0.1 dex. \textbf{Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR. There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.}

@@

\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split difference profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0. Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers. We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.3$-$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex. The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel. Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.}

@@

In \textbf{bottom left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins. \textbf{The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0. When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair. In major mergers, the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions.}
